---
title: "R Vector operations"
author: "S M Rasool"
date: "January 20, 2018"
output:
  md_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#Creating a numeric vector

```{r}
marks <- c(33,56,43,87,96)
marks

```


#accessing a numeric vector by index 


```{r}
marks[1]

marks[c(2,5)]

marks[-c(3,5)]

```

## Plot

```{r}
plot(marks)
```


#Replacing elements by index

```{r}
marks[3] <- 66
marks

```


#length

length(marks)

#accessing the last element

marks[length(marks)]

#creating number sequence

10: 6

90: 99

#subsetting a vector

sub_marks <- marks[5:2]
sub_marks

length(marks)
last_3_marks <- marks[c(length(marks)-2:length(marks))]
last_3_marks

#first three

First_3_marks <- marks[1:3]
First_3_marks

#Vector Arithmetic

marks_with_practicals <- marks + 50
marks_with_practicals

percentage_marks<- (marks[1]+marks[2]+marks[3]+marks[4]+marks[5])/500 *100
percentage_marks


##vector + vector - Equal Size
std_paid_fee <- c(20, 40, 30, 55)
std_paid_fee
std_total_fee <- c(100,150,400,60)
std_total_fee
remaining_fee <- std_total_fee - std_paid_fee




##vector + vector - Equal Size

std_join_date <- c(2012,2011, 2000)
std_join_date
std_comp_date <- c(2017,2018)
std_comp_date
duration_student <- std_join_date + std_comp_date

#It will show warning message about length















